---
title: "Mystery Novel Project"
author: "April Zhao"
date: "10/27/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Getting the Data
The data for this project is downloaded from Project Gutenberg, with three works from each author:
**Edgar Allan Poe**

1. `masque`: The Masque of the Red Death
2. `cask`: The Cask of Amontillado
3. `usher`: The Fall of the House of Usher

**Aurthur Conan Doyle**

4. `hound`: The Hound of the Baskervilles
5. `signfour`: The Sign of the Four
6. `scarlet`: A Study in Scarlet

**Agatha Christie**
7. `links`: The Murder on the Links
8. `adversary`: The Secret Adversary
9. `styles`: The Mysterious Affair at Styles


```{r txt}
url1 <- "https://www.gutenberg.org/files/1064/1064-0.txt"
url2 <- "http://www.gutenberg.org/cache/epub/1063/pg1063.txt"
url3 <- "http://www.gutenberg.org/cache/epub/932/pg932.txt"

url4 <- "https://www.gutenberg.org/files/2852/2852-0.txt"
url5 <- "https://www.gutenberg.org/files/2097/2097-0.txt"
url6 <- "https://www.gutenberg.org/files/244/244-0.txt"

url7 <- "https://www.gutenberg.org/files/58866/58866-0.txt"
url8 <- "https://www.gutenberg.org/files/1155/1155-0.txt"
url9 <- "http://www.gutenberg.org/files/863/863-0.txt"

download.file(url1, "./text/masque.txt")
masque <- readLines("./text/masque.txt", encoding = "UTF-8")
masque <- masque[31:237]

download.file(url2, "./text/cask.txt")
cask <- readLines("./text/cask.txt", encoding = "UTF-8")
cask <- cask[33:362]

download.file(url3, "./text/raven.txt")
raven <- readLines("./text/raven.txt", encoding = "UTF-8")

```




